%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Apple SPG} % Organization
    {Cupertino, CA} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Key player in GPU cloud deployment effort. Used TritonServer, TensorRT, custom ops and other optimizations to improve performance and bring down the cost from \$20M to \$80K.}
        \item {Implemented and guided Quantization Aware Training for Deep Learning models.}
        \item {Plan roadmap and scope out projects.}
        \item {Mentoring team members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer - Tech Lead Manager} % Job title
    {Aurora Innovations} % Organization
    {Mountain View, Ca} % Location
    {Jan. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved the Inference latency of Aurora perception model by 1.7x by converting the model to TensorRT, writing custom cuda kernels and other optimizations.}
        \item {Evaluated Multi-Instance GPU in A100 for Aurora perception models.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Uber ATG} % Organization
    {San Francisco, CA} % Location
    {April 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved the training and inference performance of perception models by an average of 1.5x and 2x respectively by analyzing and optimizing multiple bottlenecks.}
        \item {Integrated TensorRT with models using Torch2TRT for Inference.}
        \item {Implemented “GroupNorm” operation as a plugin in Torch2TRT to provide a fallback path from TensorRT to PyTorch.}
        \item {Designed and Implemented Multi-streaming to launch work from multiple sensors on the autonomous vehicle on different CUDA Streams to parallelize computation and reduce inference and training time.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr Deep Learning Architect} % Job title
    {Nvidia Corp.} % Organization
    {Santa Clara, CA} % Location
    {Sept. 2017 - April 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed tool to automate the Deep Neural Network performance analysis process.}
        \item {Worked on analyzing the difference in Executed performance analysis for Automatic Mixed Precision in TensorFlow which was released at GPU Technical Conference 2019.}
        \item {Lead post-silicon performance architect for TitanRTX and T4 data center chips. Executed end-to-end training studies and improved training performance by 24\%.}
        \item {Implemented multiple features in Python based simulator to explore functionality and performance for the next gen-architecture.}
        \item {Coordinated with Framework, cuDNN/cuBLAS, Driver and Unit architecture teams to identify and resolve performance issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. ASIC Design Engineer} % Job title
    {Nvidia Corp.} % Organization
    {Santa Clara, CA} % Location
    {Feb. 2013 - Sept. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead designer of the Compute work distributor of GPU compute pipeline.}
        \item {Architected, designed and implemented simultaneous compute and graphics in multiple generations of NVIDIA GPU (Maxwell, Pascal, Volta \& Turing).}
        \item {Designed and implemented compute instruction level preemption in PASCAL architecture of NVIDIA GPU.}
        \item {Designed and implemented subcontext dynamic partitioning feature in Volta architecture.}
        \item {Worked on micro-architecture, functional and formal verification, synthesis and timing of scheduler and compute work distributor unit in NVIDIA GPUs.}
      \end{cvitems}
    }
\end{cventries}
